---
title       : Graphing Ball Motion
subtitle    : 
author      : Doroszlai, Attila
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## About

The [Ball Motion app](https://adoroszlai.shinyapps.io/ball_motion) simulates a ball thrown to the air.

```{r,echo=FALSE}
source('functions.R')
g <- 9.80665
initial_speed <- 6
angle <- 42
```

```{r,echo=FALSE}
create_plot(
  calculate_trajectory(g, initial_speed, angle),
  calculate_plot_limits(g, initial_speed)
)
```

(`r initial_speed` m/s initial speed at `r angle` degrees on the Earth)

--- 

## Purpose

The app demonstrates the relationship in this simple physical experiment between inputs:

  * initial speed
  * angle of throw
  * gravity

and outputs:

  * altitude reached
  * horizontal distance covered
  * time elapsed
  * vertical speed

--- 

## Functionality

The app draws 4 plots that dynamically adapt to user input:

  * altitude vs. horizontal distance
  * vertical speed vs. horizontal distance
  * altitude vs. time
  * vertical speed vs. time

---

## Usefulness

Users can find out answers eg. for the following questions:

  1. What is the best angle to throw the ball in order to make it land the farthest possible?
  1. Does initial speed affect the shape of the trajectory?
  1. How does the strength of gravity affect the time until the ball hits the ground?
